The Design and Implementation of the Synchronous Language \CEU

### 2016-10-02 paper.tex
(>) data dependency

Another distinction regarding event handling in comparison to \CEU is that 
Esterel supports same-cycle bi-directional 
communication~\cite{esterel.compiling}, i.e., two threads can react to one 
another during the same cycle due to mutual signal dependencies
(a.k.a. \emph{instantaneous dialogue}~\cite{rp.book}).
%
\CEU takes a different approach, posing a tradeoff that an \code{await} is only
valid for the next reaction, i.e., if an \code{await} and \code{emit} occur 
simultaneously in parallel trails, the \code{await} does not awake.
%
These \emph{delayed awaits} avoid corner cases of instantaneous termination and 
re-execution of statements in the same reaction (known as \emph{schizophrenic 
statements}~\cite{esterel.constructive}).

TODO: mesmo sem mutual dependency, falar de semantica construtiva e lei da
coerencia

@@

Esterel has different compilation back ends that synthesizes to software and 
also to hardware circuits~\cite{esterel.emperor,esterel.tutorial}.
Among the software-based approaches,
\emph{SAXO--RT}~\cite{esterel.saxort,esterel.efficient} is the closest to our
implementation with respect to trail allocation and scheduling:
the compiler slices programs into ``control points'' (analogous to our ``entry 
points'') and rearranges them into a directed acyclic graph respecting the 
constructive semantics of Esterel.
Then, it flattens the graph into sequential code in \C suitable for static 
scheduling.

TODO: compilação mais sofisticada, tem que lidar com data dependency

>>>>

Another distinction regarding event handling in comparison to \CEU is that 
Esterel supports same-cycle bi-directional 
communication~\cite{esterel.compiling}, i.e., two threads can react to one 
another during the same cycle due to mutual signal dependencies
(a.k.a. \emph{instantaneous dialogue}~\cite{rp.book}).
%
\CEU takes a different approach, posing a tradeoff that an \code{await} is only
valid for the next reaction, i.e., if an \code{await} and \code{emit} occur 
simultaneously in parallel trails, the \code{await} does not awake.
%
This approach avoids any form of graph construction or data dependency analysis
as required in Esterel, e.g.:
``set or reset of a signal must always precede any test of this signal (signal
coherence law and constructivity''~\cite{esterel.saxort}.
%
Also, these \emph{delayed awaits} avoid corner cases of instantaneous
termination and re-execution of statements in the same reaction (known as
\emph{schizophrenic statements}~\cite{esterel.constructive}).

@@

Esterel has different compilation back ends that synthesizes to software and 
also to hardware circuits~\cite{esterel.emperor,esterel.tutorial}.
Among the software-based approaches,
\emph{SAXO--RT}~\cite{esterel.saxort,esterel.efficient} is the closest to our
implementation with respect to trail allocation and scheduling:
the compiler slices programs into ``control points'' (analogous to our ``entry 
points'') and rearranges them into a directed acyclic graph.
Then, it flattens the graph into sequential code in \C suitable for static 
scheduling.
Esterel compilation is more sophisticated since it involves solving data
dependency relations to comply with its constructive semantics.
